Postural developments mediate children's visual access to social information

### 2018-01-29 writeup-cogsci/cogsci2018_faceOnly_alessandro.Rmd
add conf intervals

```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion face and wrist/hand detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture."}

>>>>

```{r detByNaming, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=3, fig.height=3, fig.cap = "Proportion face and wrist/hand detections around a naming instance ('Look, a Zem'; +/- 2 seconds around each utterance) as a function of infants' posture. Error bars represent non-parametric bootstrapped 95% confidence intervals."}
